A simplified dynamic bioenergetic model for coral-*Symbiodinium* symbioses and coral bleaching as an alternate stable state

### 2017-01-10 JTB_supp/JTB_supp.Rmd
replace Fig S9 with hysteresis under N/X regimes

# Figure S9. Overshoot of symbiont density following bleaching.
```{r FigS9, cache=T}
# Set run time vector
time <- seq(-100, 1095, 0.1)  # if single model run, use time input

# Initialize environment
env <- init_env(time=time, L=c(60,20,4), N=c(2e-7,2e-7,0), X=c(2e-6,2e-6,0))

# Set parameters
defpars <- def_pars()  # Get default parameters

# Run simulation
run <- run_coral(time=time, env=env, pars=defpars)
plot_run(run)
```

>>>>

# Figure S9. Hysteresis under different nutrient and feeding regimes.
```{r FigS9, cache=T}
# Set up cluster for parallel processing
cl <- makeCluster(detectCores())  # Initiate cluster
registerDoParallel(cl)

# Set input values for steady state runs
input <- expand.grid(L=seq(20,55,1), initS=c(0.0001,0.1))

# Run steady states in parallel
output1 <- foreach(i=1:nrow(input), .combine=rbind) %dopar% {
  run <- run_coral_ss(env=list(L=input$L[i], X=2e-6, N=1e-7), pars=replace(defpars, "initS", input$initS[i]), dt=0.1)
  list(gr=last(run$H$dH.Hdt), sh=last(run$S$S/run$H$H))
}

output2 <- foreach(i=1:nrow(input), .combine=rbind) %dopar% {
  run <- run_coral_ss(env=list(L=input$L[i], X=1e-6, N=1e-7), pars=replace(defpars, "initS", input$initS[i]), dt=0.1)
  list(gr=last(run$H$dH.Hdt), sh=last(run$S$S/run$H$H))
}

output3 <- foreach(i=1:nrow(input), .combine=rbind) %dopar% {
  run <- run_coral_ss(env=list(L=input$L[i], X=2e-6, N=1e-6), pars=replace(defpars, "initS", input$initS[i]), dt=0.1)
  list(gr=last(run$H$dH.Hdt), sh=last(run$S$S/run$H$H))
}

output4 <- foreach(i=1:nrow(input), .combine=rbind) %dopar% {
  run <- run_coral_ss(env=list(L=input$L[i], X=4e-6, N=1e-6), pars=replace(defpars, "initS", input$initS[i]), dt=0.1)
  list(gr=last(run$H$dH.Hdt), sh=last(run$S$S/run$H$H))
}

# Collect results
res1 <- cbind(input, output1)
res2 <- cbind(input, output2)
res3 <- cbind(input, output3)
res4 <- cbind(input, output4)

# Create plot
par(mfrow=c(2,2))

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
points(c(48,48,53,53), c(0.12,0.13,0.12,0.13), pch=c(19,1,19,1), cex=c(0.4,1,0.4,1), col=c("black","black","red","red"), xpd=T)
text(38, 0.125, labels="init. S:H", xpd=T, cex=0.7, srt=90)
text(46, c(0.12,0.13), labels=c("0.1", "0.0001"), xpd=T, pos=2, cex=0.7)
text(50, 0.15, labels=c("Steady state growth"), xpd=T, cex=0.7)
text(c(48,53), 0.14, labels=c("pos.", "neg."), xpd=T, cex=0.7)
apply(res1, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
apply(res2, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
apply(res3, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

plot(NA, xlim=c(20,55), ylim=c(0,0.15), xlab="Light", ylab="Steady state S:H ratio")
apply(res4, 1, FUN=function(x) {
  with(x, points(L, sh,
                 col=ifelse(gr>0, "black", "red"), 
                 pch=ifelse(initS==1e-01, 19, 1), 
                 cex=ifelse(initS==1e-01, 0.4, 1)))
})

dev.off()
```
